Cognitive Context: Impact on the Perception of a Robot

### 2015-10-29 main.tex
Removed overview of experimental procedure
Do not mention the pilot study

Figure~\ref{course_of_study} gives an overview of the protocol, detailed
hereafter.

\begin{tikzpicture}[
    >=latex,
    every edge/.style={<-,draw, very thick},
    every node/.style={draw, text centered, text width=5cm}]

    \node (n1) at (0,0) {Consent form};
    \node (n2) [below=of n1] {Familiarization}
        edge (n1);
    \node (n3) [below=of n2] {Pre-questionnaire}
        edge (n2);
    \node (n4) [below=of n3] {Videos}
        edge (n3);
    \node (n5) [below=of n4] {Post-questionnaire}
        edge (n4);

\end{tikzpicture}
    \caption{Overview of the course of the study}
    \label{course_of_study}
\end{figure}
\paragraph{Participants}

We ran first a pilot study with 10 participants, followed by an experiment with
56 subjects (mean age: 20.9, $SD=3.9$, 31 females and 25 males).
The participants were recruited amongst students of our university. To avoid
students with a high familiarity with robots and artificial intelligent systems,
Computer Science and Electronics curriculum were excluded. This was \textit{a
posteriori} comforted by the questionnaire responses: no participants
reported itself as being very familiar with robots, 8 reported some familiarity
and 7 out of 56 owned a domestic robot (vacuum cleaner).

>>>>

%Figure~\ref{course_of_study} gives an overview of the protocol, detailed
%hereafter.
%
%\begin{figure}[ht]
%\centering
%
%\begin{tikzpicture}[
%    >=latex,
%    every edge/.style={<-,draw, very thick},
%    every node/.style={draw, text centered, text width=5cm}]
%
%    \node (n1) at (0,0) {Consent form};
%    \node (n2) [below=of n1] {Familiarization}
%        edge (n1);
%    \node (n3) [below=of n2] {Pre-questionnaire}
%        edge (n2);
%    \node (n4) [below=of n3] {Videos}
%        edge (n3);
%    \node (n5) [below=of n4] {Post-questionnaire}
%        edge (n4);
%
%\end{tikzpicture}
%    \caption{Overview of the course of the study}
%    \label{course_of_study}
%\end{figure}
\paragraph{Participants}

We ran the experiment with 56 subjects (mean age: 20.9, $SD=3.9$, 31 females and
25 males).  The participants were recruited amongst students of our university.
To avoid students with a high familiarity with robots and artificial intelligent
systems, Computer Science and Electronics curriculum were excluded. This was
\textit{a posteriori} comforted by the questionnaire responses: no participants
reported itself as being very familiar with robots, 8 reported some familiarity
and 7 out of 56 owned a domestic robot (vacuum cleaner).
